%------------------------------------------------------------------------------
%
%	abstract.tex General monetary system part
%
%	INCLUDE FILE FOR LaTeX2e DOCUMENT
%
%	AUTHOR: Ari Potkonen /JARVENPAA/ Mon Jun 28 2022
%------------------------------------------------------------------------------
%         1         2         3         4         5         6         7
%123456789012345678901234567890123456789012345678901234567890123456789012345678
%-BEGIN OF INCLUDE FILE--------------------------------------------------------
%\part{Abstract}
%\begin{abstract}
Daily tax\hspace*{\fill}
\linebreak
Back cover abstract\hfill
%\addcontentsline{toc}{chapter}{Abstract}
%\index{abstract}
\label{abstract}
\linebreak

This booklet looks possibility to create and use 356 day sliding window taxation
in real life as national income tax system.
While daily tax can be negative, and allow daily income,
it makes possible to think social security support new way.
Temporary and zero hour work agreements are easier to accept with the daily tax
because if you don't have income on certain period,
then negative daily tax guarantee some small daily income amount to your account.
This also helps students, pensioners etc. to take small jobs which increase they income
but don't change they work life status or cause any hiccup with official agreements.
It's also good for people having problems to get monthly payment divided so
that there are some money left at the end of period before next payment.
Daily tax process deliver some small amount to account on every day.
When payment is arriving then income is divided to period and taxes are taken,
but before next payment negative tax brings every day something into account.
Again when payment comes,
daily tax rise to positive and after tax is taken rest is left to account.
%\end{abstract}
%-END OF INCLUDE FILE----------------------------------------------------------
