%------------------------------------------------------------------------------
%
%	afterwrd.tex Document preface part
%
%	INCLUDE FILE FOR LaTeX2e DOCUMENT
%
%	AUTHOR: Ari Potkonen /JARVENPAA/ Mon Jun 28 2022
%------------------------------------------------------------------------------
%         1         2         3         4         5         6         7
%123456789012345678901234567890123456789012345678901234567890123456789012345678
%-BEGIN OF INCLUDE FILE--------------------------------------------------------
%\addcontentsline{toc}{chapter}{Afterwords}
\chapter{Afterwords}
\index{afterwords}
\label{afterwords}
Child's right\cite{ChildProtectionCrisis}
is to have possibility to have childcare - infant school education,
therefore basic daycare costs should be integrated to child's own support as well
child's part from homing benefit has to be integrated to child's own benefit.
This significantly reduce effective marginal tax and parents stress because
they can take work without drawbacks because parent income does not reduce child's benefit.
This way daily tax remove barriers and encourage peoples to stay active,
productive and give support immediately when needed without any bureaucracy.

When looking single adults without kids and any other income than included support,
we notice that even daily tax guarantee some daily income, and reduce bureaucratic load,
peoples are still very vulnerable situation to live with this level income.
Possible problems like rapidly changed energy price for example,
or from bad consumption selections like using consumer credit which increase cost
and rapidly leads to sold dept and dept collection by third party
adding more extra cost over original dept.
They deliver paper invoices during due date to mailboxes,
automatically generating significant extra cost if not paid in hours.
Therefore, there has to be legal mechanism
%\cite{LEX_2023_186}\-\cite{ConsumerCreditAndMicroloanCompanies}[?]
to limit dept
and it's collection costs to 120\% from original dept,
force collector use official electric messaging platform to reach peoples
and have official log from they messages timing,
besides paper invoices delivered on due date more or less purposefully.
This legal limitation leads to situation where overall economy has meaning
and it's not possible just to transfer extra business profit making costs over citizen.
When limit is filled it's paid no matter how many claims are sent after that.
%-END OF INCLUDE FILE----------------------------------------------------------
