%------------------------------------------------------------------------------
%
%	preface.tex Document preface part
%
%	INCLUDE FILE FOR LaTeX2e DOCUMENT
%
%	AUTHOR: Ari Potkonen /JARVENPAA/ Mon Jun 28 2022
%------------------------------------------------------------------------------
%         1         2         3         4         5         6         7
%123456789012345678901234567890123456789012345678901234567890123456789012345678
%-BEGIN OF INCLUDE FILE--------------------------------------------------------
%\chapter{Preface}
PREFACE
%\addcontentsline{toc}{chapter}{Preface}
%\index{preface}
\label{preface}

\vskip\baselineskip
As I have been quite long time Finnish citizen I have been seeing later
development, what it does when preemptive support for peoples, families and
children's heath, education and social care has been reduced year by year. Now
lot of money goes to care serious results from this habit and grown average
age. Worst thing here is that caring problems and re-enabling preemptive care
with current system and existing maintenance ratio goes over budget if nothing
else is done. And many peoples own budget has already failed partly because we
as society has been allowed to sell out and therefore from local monopoles for
electric delivery and significantly determinative market positions on rentable
property, housing and apartments market. Besides these there are IT and goods
logistic costs having external cream pealers groups on significant market
position. These areas are used to squeez money out from our society, it's
partly increased peoples support need, and this has been led to higher support
during the years, support which is now teared down. Problem is that peoples are
now left between profitmakers demands and subventions closing sosiety created
realities. We could already say that shit has hit into fan.
% and smell lingers around badly.
Overloaded, less paid healthcare workers are already escaping from profession
area\allowbreak\cite{KEVA_tyovoimaennuste}, medical institutions see declining
amount of applicants to profession area courses\allowbreak\cite{
 YLE202209221026}. Teachers comment seriously that if knew current situation on
work market when started studies did not choosed to become a teacher. Etc.

\vskip\baselineskip
How we came to this situation at 2023 ?
\vskip\baselineskip
When looking national law making which does basement for Finnish wellbeing
 society we need to note one bad habit we have. To maintain wellbeing society
new laws are nearly always made as small tweaks to existing law by adding new
law section, new on/off-rule or rules. After years of this kind of operation
the result is awful for normal citizens. It is mess of "on/off, on/off, if then
else on/off,..." rules. It's nightmare for people having scarce resources and
need for help. Especially people lacking good digital information search,
bookkeeping and management capabilities is in really deep shit! Fin\-nish
nation has help-begging system for pen, paper and physical access peoples, and
for others\allowbreak\cite{StudentHousingAllowance}, it's resource consuming
and inhumane. You are really pushed down before you can get anything, if even
then\allowbreak\cite{KELA_BASIC_ASSISTANCE_HalfOrNone}. Finnish mental health
and suicide statistics tell the truth\allowbreak\cite{SurunauhaTilastot} from
less performed peoples status. It's quite raw statistics: about four times more
suicides per year\allowbreak\cite{CausesOfDeath} than what dies at same time to
traffic accidents\allowbreak\cite{RoadAccidentStatistics}. According to world
happiness report\allowbreak\cite{WHR2023} happiest country is Finland.
Happiness do not touch all citizens of Finland. Nation doesn't really support
peoples when they need help. To get help on time you have to be
preemptive\allowbreak\cite{KELATargetTime} by yourselves\allowbreak\cite{
 Yle202412141253} and have some resources left\allowbreak\cite{
 KELAProcessingTime}. Most peoples who really need help don't be that level
systematic, or have lost they touch, for reason or other. After loosing life
control there are too many paid "No", "Wait", "Fill this", "Forward to", "It
takes a while", "Later", ..., -naysayers, paid officials\allowbreak\cite{
 KELApalvelee}\allowbreak\cite{
 KELA_BASIC_ASSISTANCE_HalfOrNone}\allowbreak\cite{VR23_SocialBenefitsComics},
or created automations, transfer the burden of proof\allowbreak\cite{
 BurdenOfProof} to the customer\allowbreak\cite{StudentHousingAllowance}, and
same time exploitation companies; private dept collection agency's do they best
to hook people\allowbreak\cite{MOT_VelkaantuneidenVastaisku} who had to have
from 9.3\allowbreak\cite{KELA_StudyGrant} to 18.5\euro/d\allowbreak\cite{
 KELA_BASIC_ASSISTANCE} for bigger problems and make profit while people is
temporalily insolvent due delays in process, where quick quotation companies
try also abuse, sell they money with 35\%\allowbreak\cite{
 ConsumerCreditAndMicroloanCompanies} average interest. This easily leads to
personal backrupt, juridiciary\allowbreak\cite{MOT_VelkaantuneidenVastaisku}
and National Enforcement Authority\allowbreak\cite{
 NationalEnforcementAuthorityFinland} even supports private collections agency
to make profit\allowbreak\cite{PaymentDefaultStatistics}, and results are
really obvious, brutal -- deeply not wellbeing peoples, eating psychoactive
drugs\allowbreak\cite{DepressionValidTreatment} as daily
bread\allowbreak\cite{YLE202112131842}\allowbreak\cite{
 YLE202305170931}\allowbreak\cite{YLE202311120715}\allowbreak\cite{
 STM_UglyNumbers20230703}. %\allowbreak\cite{YLE201208241434}
When peoples finally get this "help" it's outdated, late\allowbreak\cite{
 PosCredReg}, not informed and not to original problem but more for
 consequences \allowbreak\cite{YLE202112131842}\allowbreak\cite{
 SocialLend}\allowbreak\cite{MOT_VelkaantuneidenVastaisku} to fail fix the
original problem.

Finnish society also thinks employee development always from current employer
perspective. Which many times is wrong perspective, because need to development
under existing employer service usually comes from need to change from current
work to something other. And then it is "fifty-sixty" old versus new employer
what is needed. Usually it's 100\% of employee own need to develop itself to be
relevant, capable to continue further on working life at current life and
health situation\allowbreak\cite{TR_202306151300}. It might be same employer's
task, but as well it can be something else, other employer, third sector,
entrepreneur, research,... what ever, but so that peoples can maintain they
health and control to they own life. This is partly understood\allowbreak\cite{
 VN_202303241233}, but not fully\allowbreak\cite{
 AdultEducationAllowance}\allowbreak\cite{VN_2023/58}.

Current system has these on/off -flaws which make peoples to be out of working
life, working 0\% or full 110\% working life to be able to carry economic
burden we have. There are not many good possibilities between these two
choices. There should be whole variation of working life load levels here
between these 0\% and 110\% really! And there isn't!

\vskip\baselineskip
What we can do for this existing not so great legacy?
\vskip\baselineskip
We can't really fully solve all these problems, but can give advice how to
empower peoples to care themselves more with less by reducing they mental,
financial and physical resources load\allowbreak\cite{KELA_BASIC_ASSISTANCE},
giving them more control with less of operational cost. Solution is sliding 365
days window daily tax with tax curves (fittings, functions) depended on age,
capable to deliver child benefit, study grant, basic income support, home care
allowance, basic sick leave allowance, rehabilitation allowance, unemployed
basic allowance, adult education benefit and housing allowance. Those are
merged seamlessly into system behind the scenes into curves without any action
needed, not setting any income traps for anyone. This setup guarantees some
income every day, because benefits or "negative tax" is paid daily into account
until period actual wage payment comes, which is taxed taking in the account
already paid "negative tax" during the period day. And curve is designed so
that every euro in income increase net income after tax. There will be less
effective income traps from other support forms than before because of merging
and directing correctly child's benefits to the
child\allowbreak\cite{VN_2025_22}. Parent, caretaker only manages these for the
child.

Current government want to get more with less. Automatically delivered basic
support suits well to social security reform\allowbreak\cite{STM_202306021239}
project start time and government saving targets\allowbreak\cite{VN_2023/58}.
Automated delivery trustfulness, timely accuracy, without locking, is more and
more meaningful, when paid sums purchasing power is going to decline, be
smaller than before. Therefore basic monetary support delivery has to be
automated whitout any human factors in it, to get it delivered correctly on
time without delays!

Actual document goes guite straightly to proposal details, checks existing
renoval and other documentation material then does corrections to proposal,
generalizes and extends it towards more straight automated solution, then
finally is existing implementation documentation looked and commented a bit.
\vskip\baselineskip
Booklet meaning is to raise debate from existing digitized tax, etc. process
digitalization ;-). Hopefully you get some ideas from here for life, or for
your further professional life discussons!\hfill\break
\vskip\baselineskip
Sincerely yours, Ari Potkonen
\vspace*{\fill}
%-END OF INCLUDE FILE----------------------------------------------------------
